# Ineqaulity task - week 4

## Reproduce 

### package versions

```{r}
# i have taken a snapshot with
install.packages("renv")
renv::snapshot()

#install the same packages
renv::restore()
```
### Read in data:

Located within the Data folder:

* HDI data from: http://hdr.undp.org/en/indicators/68606#
* Shapefile from: https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41 

## Load packages
```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
library(countrycode)
library(Rcpp)
library(maptools)
library(RColorBrewer)
library(classInt)
library(sp)
library(rgeos)
library(tmap)
library(tmaptools)
library(sf)
library(rgdal)
library(geojsonio)
library(readr)
library(tidyverse)
library(janitor)
library(OpenStreetMap)

```

```{r}
HDI <- read_csv(here::here("Data", "Gender Inequality Index (GII).csv"),
                       locale = locale(encoding = "latin1"),
                       na = "..", skip=0)
World <- st_read(here::here("Data", "World_Countries__Generalized_.shp"))
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column 

```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(country, x2019, x2010)%>%
  mutate(difference=x2019-x2010)%>%
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))

#this was just a test. 
#t <- countrycode(HDIcols$country, origin = 'country.name', destination = 'iso2c') 

```

## Join

Join the csv to world shape file

```{r}
Join_HDI <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("aff_iso" = "iso_code"))
```
## Clean data

Delete the columns which has "N/A" or other useless data
```{r}
Join_HDI_tidy <- Join_HDI %>%
  filter(difference != "NA")  #剔除无用数据
```

...next time 
```{r}
tmap_mode("plot")
qtm(Join_HDI_tidy, 
    fill = "difference")

tmapJoin_HDI_tidy <- Join_HDI_tidy %>%
  st_bbox(.) %>% 
  tmaptools::read_osm(., type = "osm", zoom = NULL)

tm_shape(tmapJoin_HDI_tidy)+
  tm_rgb()+
  tm_shape(Join_HDI_tidy) + 
  tm_polygons("difference", 
              style="pretty",
              palette="YlOrBr",
              midpoint=NA,
              title="Difference in GII",
              alpha = 0.6) + 
  tm_compass(position = c("left", "bottom"),type = "arrow") + 
  tm_scale_bar(position = c("left", "bottom")) +
  tm_layout(title = "Gender Inequality Index Difference Between 2010 and 2019", legend.position = c("right", "bottom"))
```


